\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-15 paper/figures.tex
add future work

\newcommand{\TabCompare}{
\begin{table*}[t]
    \centering
    \begin{tabular}{l|cccccccc}
            % Multiflow? Waterfall?
            & \rot{Telex~\cite{telex11}} &
            \rot{Cirripede~\cite{cirripede11}} &
            \rot{Decoy Routing~\cite{curveball11}} &
            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall17}} & \rot{\textbf{\scheme}} \\
            \hline
                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
            Handles asym. routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
            Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
            Traffic analysis resitant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
            Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
    \end{tabular}
    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,}
    \label{tab:compare}
\end{table*}
}

>>>>

\newcommand{\TabCompare}{
\begin{table*}[t]
    \centering
    \begin{tabular}{l|cccccccc}
            % Multiflow? Waterfall?
            & \rot{Telex~\cite{telex11}} &
            \rot{Cirripede~\cite{cirripede11}} &
            \rot{Decoy Routing~\cite{curveball11}} &
            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall17}} & \rot{\textbf{\scheme}} \\
            \hline
                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
            Handles asym. routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
            %Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
            Traffic analysis resitant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
            %Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
            Unlimited Session Length  &\yes & \yes & \yes & \no  & \no  & \no  & \no  & \yes \\
            %Multicore Implementation  &\no  & \no  & \no  & \yes & \no  & \no  & \no  & \yes \\
    \end{tabular}
    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,}
    \label{tab:compare}
\end{table*}
}

### 2019-02-15 paper/paper.tex
add future work

\subsubsection{WebRTC}

@@

\TODO{Write (0.5 page)}

>>>>

\subsubsection{WebRTC}
\label{sec:webrtc}

@@

\scheme provides a much larger degree of engineering flexibility than previous
Refraction Networking schemes. Due to its modular design, different registration
protocols and applications can be used. One obvious direction is to further
study such alternatives. For instance, while we use a TapDance-like
registration, we could potentially cut down on the overhead of one-time
registration by using port-knocking or using a Telex-style~\cite{telex11} tag (in the Client
Hello rather than Application Data).

\paragraph{Client-side applications}
On the application side, \scheme provides an interesting opportunity to explore
\emph{client mimicking} dark decoys. Rather than pretend to be a server (e.g.
mask site), our application could connect back to a client after registration
from the dark decoy address. Protocols like WebRTC mentioned in
Section~\ref{sec:webrtc} or other peer-to-peer protocols such as BitTorrent,
Skype, or Bitcoin.

\paragraph{Traffic Analysis}
\scheme could also support applications that tradeoff performance for
observability. While Slitheen offers ideal mimicry of decoys, it comes at a high
cost of overhead. \scheme mask site applications could implement Slitheen
in order to perfectly mimic the mask site's latency, packet timings, and payload
sizes. In addition, careful choice of mask sites may allow for higher
performance, as sites with more replaceable content can carry more covert data.

\paragraph{Long-term Deployment}
Ultimately, the goal for Refraction Networking protocols is to be useful in
circumventing censorship. While it has taken many years for research
protocols to mature, we are excited to see schemes like TapDance deployed in
practice~\cite{frolov2017isp}. We believe \scheme can be even easier to deploy
at scale, and hope to leverage the existing success of TapDance to place \scheme
stations in real-world ISPs.
